Article - Figures

### 2020-07-29 article_figures_FLORIAN_RICOUR.Rmd
clean and update

# EACH PROFILES HAS BEEN VALIDATED SO FAR ==> CALIBRATION EXERCISE STARTS NOW
# LET'S DO IT ONLY FOR THE DEEP PROFILE
# FDOM-based method (Xing et al. 2017)
# keep only the validation profile 
data <- data[data$id == 3,]
data_info <- clean_remove(data_info, unique(data$juld))
MLDdf <- clean_remove(MLDdf, unique(data$juld))
data <- transform(data,id=as.numeric(factor(juld)))

>>>>

# EACH PROFILES HAS BEEN VALIDATED SO FAR
data <- data[data$id == 3,]
data_info <- clean_remove(data_info, unique(data$juld))
MLDdf <- clean_remove(MLDdf, unique(data$juld))
data <- transform(data,id=as.numeric(factor(juld)))
